---
title: "Forecasting Report"
author: "by Nicholas Reimold - `r format(Sys.time(), '%B %d, %Y  %I:%M %p')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: 
      collapsed: false
      smooth_scroll: true
params:
    pathMaster:  "C:/Users/A4034/Desktop/ModelEvaluation/NewFolder"
---

<style>
#TOC {
  top: 1%;
  opacity: 0.5;
}
#TOC:hover {
  opacity: 1;
}

body .main-container {
max-width: 1800px;
}
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(plotly)
library(xfun)
library(data.table)
library(dplyr)
library(pROC)
library(splitstackshape)
library(kableExtra)
library(lubridate)
library(rmarkdown)
library(funModeling)
library(formattable)
library(dlookr)
library(knitr)
library(shiny)

options("scipen"=999)
pathMaster <- params$pathMaster


load(file.path(pathMaster,"ForecastMetricData.RData"))
```




# Methodology
***
```{r,results='asis',layout="l-body-outset",echo=FALSE,message=FALSE,warning=FALSE}

format.money  <- function(x, ...) {
    paste0("$", formatC(as.numeric(x), format="f", digits=0, big.mark=","))
}

DES=NULL
for (j in 1:length(RESULTS)){
xx=RESULTS[[j]]%>%group_by(Window,Prod)%>%summarise(
                                   Accounts=sum(Accounts),
                                   Pred.Losses=sum(Pred.Losses))%>%mutate(DQ.Status="Overall")

DES=DES%>%rbind(DescriptionDF%>%mutate(Losses=xx$Pred.Losses[1],ScenarioID=j))
}
DES%>%
  kable(escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),font_size = 12)
```



***
# Total Losses by Scenario  {#buttons .tabset .tabset-fade .tabset-pills}
***

```{r,results='asis',echo=FALSE,fig.align='center',message=FALSE,warning=FALSE}

DES=NULL
for (j in 1:length(RESULTS)){
xx=RESULTS[[j]]%>%group_by(Window,Prod)%>%summarise(
                                   Accounts=sum(Accounts),
                                   Pred.Losses=sum(Pred.Losses),
                                   Balance=sum(Balance))%>%mutate(CoverageRatio=Pred.Losses/Balance,DQ.Status="Overall")

RESULTS2=RESULTS[[j]]%>%mutate(CoverageRatio=Pred.Losses/Balance)%>%full_join(xx)%>%
  mutate(Pred.Losses=format.money(Pred.Losses),
         Balance=format.money(Balance),ScenarioID=j)

names(RESULTS2)<-c("Window","Product","DQ Status","Number of Accounts","Predicted Losses","ScenarioID")

 cat('\n## ID = ', j, '\n')

R=kable(RESULTS2) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),font_size = 12)
print(R)
}


```


# Losses over Time {#buttons .tabset .tabset-fade .tabset-pills .columnsection}
***

```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE,eval=TRUE}
titles=c("Time Point Loss","Cumulative Loss")
plotlist=list()
for(j in 1:2){
      DF=NULL

  for(qq in 1:length(OverallTimePoint)){
    a=OverallTimePoint[[qq]]%>%group_by(Time)%>%summarise(Pred.Loss=sum(Pred.Loss/1000000))
    if(j==2){
      a=a%>%mutate(Pred.Loss=cumsum(a$Pred.Loss))
    }
    names(a)[2]<-paste0("ID=",qq)
    if(is.null(DF)){
      DF=a
    }else{DF=DF%>%full_join(a)}
  }
      
d=reshape2::melt(DF,id="Time")%>%rename(Scenario=variable)
  p<-ggplot(d, aes(x=Time, y=value, group=Scenario, color=Scenario)) +
    geom_line()+
    # geom_point(aes(color="#e9ecef"))+ 
    theme_minimal() +
    theme(
      plot.title = element_text(size=20),
      axis.text=element_text(size=12),
      axis.title = element_text(size=15)
    )+ #theme(legend.position="none")+
    ggtitle(titles[j])+labs(y="Predicted Losses(Millions)",x="Months afer Snapshot")
                   plotlist[[j]]=ggplotly(p ,tooltip=c("Time","value","Scenario"))
}
htmltools::tagList(setNames(plotlist,NULL))


```

# Losses By Bucket {#buttons .tabset .tabset-fade .tabset-pills .columnsection}
***

```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE,eval=TRUE}
titles=c("Time Point Loss")
plotlist=list()
for(j in 1){
      DF=NULL

  for(qq in 1:length(OverallTimePoint)){
    a=OverallTimePoint[[qq]]%>%group_by(Time,DQ.Status)%>%summarise(Pred.Loss=sum(Pred.Loss/1000000))
    if(j==2){
      a=a%>%mutate(Pred.Loss=cumsum(a$Pred.Loss))
    }
    names(a)[3]<-paste0("ID=",qq)
    if(is.null(DF)){
      DF=a
    }else{DF=DF%>%full_join(a)}
  }
      
d=reshape2::melt(DF,id=c("Time","DQ.Status"))%>%rename(Scenario=variable)%>%mutate(IDVAR=paste(Scenario,DQ.Status,sep="_"))
  p<-ggplot(d, aes(x=Time, y=value, group=IDVAR, color=IDVAR)) +
    geom_line()+
    # geom_point(aes(color="#e9ecef"))+ 
    theme_minimal() +
    theme(
      plot.title = element_text(size=20),
      axis.text=element_text(size=12),
      axis.title = element_text(size=15)
    )+ #theme(legend.position="none")+
    ggtitle(titles[j])+labs(y="Predicted Losses(Millions)",x="Months afer Snapshot")
                   plotlist[[j]]=ggplotly(p ,tooltip=c("Time","value","Scenario"))
}
htmltools::tagList(setNames(plotlist,NULL))


```

# Losses Rates By Bucket {#buttons .tabset .tabset-fade .tabset-pills .columnsection}
***

```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE,eval=TRUE}
titles=c("Loss Rate By Bucket")
plotlist=list()
for(j in 1){
      DF=NULL

  for(qq in 1:length(OverallTimePoint)){
    a=OverallTimePoint[[qq]]%>%group_by(Time,DQ.Status)%>%summarise(Pred.Loss=sum(Pred.Loss),EAD=sum(EAD))
    if(j==2){
      a=a%>%mutate(Pred.Loss=cumsum(a$Pred.Loss))
    }
    
    if(is.null(DF)){
      DF=a
    }else{DF=DF%>%full_join(a)}
  }
      
            DF2=NULL

    DF2=HistoricalCurve%>%group_by(Time,DQ.Status)%>%summarise(Pred.Loss=sum(CO),EAD=sum(CO=sum(BAL)))%>%mutate(PCT=100*Pred.Loss/EAD)%>%select(-Pred.Loss,-EAD)
           names(DF2)[3]<-paste0("HistoricalRates")

        
            
      DF=DF%>%mutate(PCT=100*Pred.Loss/EAD)%>%select(-Pred.Loss,-EAD)
       names(DF)[3]<-paste0("ID=",qq)
       DF=DF%>%left_join(DF2)
       DF[is.na(DF)]=0
   
d=reshape2::melt(DF,id=c("Time","DQ.Status"))%>%rename(Scenario=variable)%>%mutate(IDVAR=paste(Scenario,DQ.Status,sep="_"))
  p<-ggplot(d, aes(x=Time, y=value, group=IDVAR, color=IDVAR)) +
    geom_line()+
    # geom_point(aes(color="#e9ecef"))+ 
    theme_minimal() +
    theme(
      plot.title = element_text(size=20),
      axis.text=element_text(size=12),
      axis.title = element_text(size=15)
    )+ #theme(legend.position="none")+
    ggtitle(titles[j])+labs(y="Loss Rate(%)",x="Months afer Snapshot")
                   plotlist[[j]]=ggplotly(p ,tooltip=c("Time","value","Scenario"))
}
htmltools::tagList(setNames(plotlist,NULL))



```




***

# Loss Rates {#buttons .tabset .tabset-fade .tabset-pills .columnsection}
***


```{r,results='asis',echo=FALSE,message=FALSE,warning=FALSE,eval=TRUE}
titles=c("Historical Loss Rate","Forecasted Loss Rate")
xlabs=c("Date","Months afer Snapshot")
plotlist=list()

for(j in 1:2){
  
if(j==1){
     a=Total%>%na.omit()%>%rename(Time=Date)
           p<-ggplot(a, aes(x=Time, y=Loss_Rate)) +
        geom_line(aes(color="#69b3a2"))+
       # geom_point(aes(color="#e9ecef"))+ 
        theme_minimal() +
        theme(
          plot.title = element_text(size=20),
          axis.text=element_text(size=12),
          axis.title = element_text(size=15)
        )+ theme(legend.position="none")+
                ggtitle(titles[j])+
               labs(y="Forecasted Loss Rate(%)",x=xlabs[j])

                         plotlist[[j]]=ggplotly(p,tooltip =c("Time","Loss_Rate") )


}else{
     DF=NULL

  for(qq in 1:length(OverallTimePoint)){
     a=OverallTimePoint[[qq]]%>%group_by(Time)%>%summarise(Pred.Loss=sum(Pred.Loss),EAD=sum(EAD),Loss_Rate=100*Pred.Loss/EAD)%>%select(Time,Loss_Rate)
    
    names(a)[2]<-paste0("ID=",qq)
    if(is.null(DF)){
      DF=a
    }else{DF=DF%>%full_join(a)
    }
    
  }
     
         
d=reshape2::melt(DF,id="Time")%>%rename(Scenario=variable)
  p<-ggplot(d, aes(x=Time, y=value, group=Scenario, color=Scenario)) +
    geom_line()+
    # geom_point(aes(color="#e9ecef"))+ 
    theme_minimal() +
    theme(
      plot.title = element_text(size=20),
      axis.text=element_text(size=12),
      axis.title = element_text(size=15)
    )+ ggtitle(titles[j])+
               labs(y="Forecasted Loss Rate(%)",x=xlabs[j])
                   plotlist[[j]]=ggplotly(p ,tooltip=c("Time","value","Scenario"))

}
   
   




}
htmltools::tagList(setNames(plotlist,NULL))


```



