---
title: "Exploratory Data Analysis Report"
author: "Report by dlookr package"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    toc: true
    number_sections: true
    theme: cayman
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r enrironment, echo=FALSE, warning=FALSE, message=FALSE}
library(xtable)
library(magrittr)
library(dlookr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(moments)
library(knitr)
library(kableExtra)
```


```{r udf, echo=FALSE, warning=FALSE, message=FALSE}
dist_numeric <- function(df, target, predictor) {
  library(dplyr)

  descr <- df %>%
    target_by(target) %>%
    relate(predictor)

  vars <- unlist(descr[, 2])

  descr <- descr %>%
    select(-c(1:2)) %>%
    t

  colnames(descr) <- vars

  descr <- descr[, rev(seq(NCOL(descr)))]

  rnames <- c("n", "NA", "mean", "sd", "se(mean)", "IQR",
              "skewness", "kurtosis")
  rnames <- c(rnames, paste0(c(0, 1, 5, 10, 20, 25, 30, 40, 50, 60, 70,
                               75, 80, 90, 95, 99, 100), "%"))
  row.names(descr) <- rnames

  as.data.frame(descr)
}


setUnder <- function(x) {
  gsub("_", ".", x)
}

edaData <- as.data.frame(get("edaData", .NRDLOOKEnv))
targetVariable <- get("targetVariable", .NRDLOOKEnv)

if (length(targetVariable) == 0) targetVariable <- NULL
```

```{r check_variables, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
idx.numeric <- find_class(edaData, type = "numerical")
idx.factor <- find_class(edaData, type = "categorical")
nm.numeric <- find_class(edaData, type = "numerical", index = FALSE)
nm.factor <- find_class(edaData, type = "categorical", index = FALSE)

if (!is.null(targetVariable)) {
  # remove target variable from variable index
  idx.numeric <- idx.numeric[nm.numeric != targetVariable]
  idx.factor <- idx.factor[nm.factor != targetVariable]
  
  factor_flag <- class(pull(edaData, targetVariable))[1] %in% c("factor", "ordered")
  numeric_flag <- class(pull(edaData, targetVariable))[1] %in% c("integer", "numeric")
  
  target <- if (!factor_flag & numeric_flag) 
    factor(pull(edaData, targetVariable)) else
      pull(edaData, targetVariable)
}

# if all elements of a numerical variable are NA,
# remove from correlation coefficient calculation
idx.numeric <- idx.numeric[apply(edaData[, idx.numeric], 2,
                                 function(x) !all(is.na(x)))]

# if all elements of the numerical variable are the same value,
# remove from the correlation coefficient calculation
idx.numeric <- idx.numeric[apply(edaData[, idx.numeric], 2,
                                 function(x) diff(range(x, na.rm = TRUE)) > 0)]

```


# Introduction
The EDA Report provides exploratory data analysis information on objects that inherit data.frame and data.frame.


## Information of Dataset
The dataset that generated the EDA Report is an **'`r class(edaData)[1]`'** object. It consists of **`r format(NROW(edaData), big.mark = ",")` observations** and **`r NCOL(edaData)` variables**.


## Information of Variables
The variable information of the data set that generated the EDA Report is shown in the following table.:
```{r info_variables, echo=FALSE, warning=FALSE, message=FALSE, comment="", results='asis'}
cap <- "Information of Variables"

vars <- edaData %>% 
  diagnose() 


knitr::kable(vars, caption = cap, format = "html") %>% 
  kable_styling(full_width = FALSE, font_size = 15, position = "left") %>% 
  cat()

target_nm <- if (is.null(targetVariable)) "NULL" else targetVariable
target_type <- if (is.null(targetVariable)) 
  "NULL(You did not specify a target variable)" else 
  class(pull(edaData, targetVariable))[1]
```

The target variable of the data is **'`r target_nm`'**, and the data type of the variable is **`r target_type`**.


## About EDA Report
EDA reports provide information and visualization results that support the EDA process. In particular, it provides a variety of information to understand the relationship between the target variable and the rest of the variables of interest.


# Univariate Analysis
## Descriptive Statistics
```{r describe_univariate, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
x <- Hmisc:::describe.data.frame(edaData)
Hmisc::html(x, file = "")
```


## Normality Test of Numerical Variables
### Statistics and Visualization of (Sample) Data
```{r normality, echo=FALSE, warning=FALSE, message=FALSE, comment="", fig.height=4, fig.width=6, results='asis'}
if (length(idx.numeric) == 0) {
  cat("\n\nThere is no numeric variable.\n\n")
} else {
  for (i in idx.numeric) {
    cap <- sprintf("%s", names(edaData)[i])
    cap <- paste(unlist(strsplit(cap, "_")), collapse = "\\_")
    
    cat("<b><font size='3' face='verdana'>[", names(edaData)[i], 
            "]</font></b>", "\n")
    
    cat("\nnormality test : Shapiro-Wilk normality test\n\n")
    
    x <- if (NROW(edaData) > 5000) {
      sample(pull(edaData, i), size = 5000, replace = TRUE)
    } else {
      pull(edaData, i)
    }
    
    if (all(is.na(x))) {
      cat("all 'x' values are NA\n\n")
      next
    }
    
    if(length(x) < 3L || length(x) > 5000L) {
      cat("sample size must be between 3 and 5000\n\n")
      next
    }
    
    if(diff(range(x, na.rm = TRUE)) == 0) {
      cat("all 'x' values are identical\n\n")
      next
    }
    
    y <- shapiro.test(x)

    cat(sprintf("\t statistic : %s,  p-value : %G\n\n",
                round(y$statistic, 5),  y$p.value))
    cat("\n<br>\n")

    skew <- c(skewness(x, na.rm = TRUE),
              skewness(log(x), na.rm = TRUE),
              skewness(sqrt(x), na.rm = TRUE))
  
    kurt <- c(kurtosis(x, na.rm = TRUE),
              kurtosis(log(x), na.rm = TRUE),
              kurtosis(sqrt(x), na.rm = TRUE))
  
    type <- c("original", "log transformation", "sqrt transformation")
    stats <- data.frame(type = type, skewness = skew, kurtosis = kurt)

    cap <- "skewness and kurtosis"
    knitr::kable(stats, caption = cap, format = "html") %>% 
      kable_styling(full_width = FALSE, font_size = 15, position = "left") %>% 
      cat()
    
    cat("\n<br>\n")
    par(mfrow = c(2, 2), mar = c(2, 4, 2, 2))
    hist(x, col = "lightblue", las = 1, main = "origin")
    qqnorm(x, main = "origin: Q-Q plot")
    qqline(x)
    hist(log(x), col = "lightblue", las = 1, main = "log")
    hist(sqrt(x), col = "lightblue", las = 1, main = "sqrt")
  
    cat("\n<hr>\n<br>\n")
  }
}  
```


# Relationship Between Variables
## Correlation Coefficient
### Correlation Coefficient by Variable Combination
```{r correlations, echo=FALSE, warning=FALSE, message=FALSE, comment=""}
if (length(idx.numeric) > 2) {
  eps <- 0.5

  cors <- edaData %>%
    correlate %>%
    filter(abs(coef_corr) >= eps) %>%
    filter(as.integer(var1) > as.integer(var2)) %>%
    arrange(desc(abs(coef_corr)))

  if (NROW(cors) > 0) {
    names(cors) <- c("Variable1", "Variable2", "Correlation Coefficient")

    cap = "Table of correlation coefficients (0.5 or more)"
    knitr::kable(cors, caption = cap, format = "html") %>% 
      kable_styling(full_width = FALSE, font_size = 15, position = "left")
  } else {
    cat("No correlation coefficient is greater than 0.5.\n\n")
  }
} else {
  cat("Number of numerical variables is less than 2.\n\n")
}
```


### Correlation Plot of Numerical Variables
```{r plot_correlations, echo=FALSE, warning=FALSE, message=FALSE, comment="", fig.height=4, fig.width=6}
if (length(idx.numeric) > 2) {
  edaData %>%
    plot_correlate()
} else {
  cat("Number of numerical variables is less than 2.\n\n")
}  
```

